XRONOS: an open data infrastructure for archaeological chronology

### 2024-11-25 paper_jcaa.qmd
Suppress sf message

```{r data-basemap}
#| warning: false
coast <- gisco_get_coastallines()
m49_regions <- gisco_get_countries() |>
  mutate(
    m49_macroregion = countrycode(ISO3_CODE, "iso3c", "un.region.name"),
    m49_subregion = countrycode(ISO3_CODE, "iso3c", "un.regionsub.name"),
    m49_intregion = countrycode(ISO3_CODE, "iso3c", "un.regionintermediate.name"),
    m49_region = coalesce(m49_intregion, m49_subregion)
  ) |>
  summarise(geometry = st_union(geometry), .by = m49_region)
```

>>>>

```{r data-basemap}
#| include: false
coast <- gisco_get_coastallines()
m49_regions <- gisco_get_countries() |>
  mutate(
    m49_macroregion = countrycode(ISO3_CODE, "iso3c", "un.region.name"),
    m49_subregion = countrycode(ISO3_CODE, "iso3c", "un.regionsub.name"),
    m49_intregion = countrycode(ISO3_CODE, "iso3c", "un.regionintermediate.name"),
    m49_region = coalesce(m49_intregion, m49_subregion)
  ) |>
  summarise(geometry = st_union(geometry), .by = m49_region)
```
